\section{Changes from previous versions}

A summary of changes introduced into \SPM\ are detailed below. These include any incremental changes, modifications, and additional functionality.

\textbf{For version \SPM\ \VER}
\begin{enumerate}
  \item Added an alternative parameterisation for the Beverton-Holt recruitment process (bh\_recruitment2)
\end{enumerate}

\textbf{For version \SPM\ 2.03-2020-08-29}
\begin{enumerate}
  \item Corrected the multinomial simulation generator for proportions-at-age and -length observations
	\item Removed the undocumented unit conversion multiplier that was in the size-weight calculations.
\end{enumerate}

\textbf{For version \SPM\ 2.02}

\begin{enumerate}
  \item Minor corrections to the user manual.
	\item Added a likelihood multiplier option to observations to modify likelihoods
	\item Added an option for including detection probabilities for proportions by category and proportions by category at length observations
	\item Speed optimisation fixes
\end{enumerate}

\textbf{For version \SPM\ 2.01}

\begin{enumerate}
  \item Updated and modified the \SPM\ build system for Git using Python3.
  \item Added R functions for reading and writing SPM configuration files
	\item Added bug fixes and consistency checking of syntax
	\item Added knife-edge selectivity function
  \item Added\ \subcommand{proportions-at-length} observations.
  \item Added\ \subcommand{growth\_proportion} to allow the size of an individual to change over the course of a year.	
  \item Updated the reports to be consistent in the output, and also updated the R extract library to account for the changes.
\end{enumerate}


